Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-03-15 manuscript.tex
Added a few more comments to manuscript

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
{When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also the changes in the shape of the CCF. Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
{We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.}
{We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels. In each case, we compare the results obtained from the Normal fitting of the CCF and from the SN fitting. We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.}
{The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN. Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity. RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity. However, once correcting the RVs from stellar activity signal using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar. The precision on the asymmetric parameter derived from the SN is also 15\% better than the one derived on the common Bisector Inverse Slope Span (BIS SPAN). Besides all these advantages, the errors on the RVs measured by the SN are 60\% greater. This is not a problem at signal-to-noise ratio levels $>$ 150 because other noise sources dominate in this regime, however we have to be careful when deriving precise RVs for low SNR measurements. We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.}
{We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.}

>>>>

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also the changes in the shape of the CCF. Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.
We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels. In each case, we compare the results obtained from the Normal fitting of the CCF and from the SN fitting. We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN. Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity. RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity. 
\comment{" interesting" is a highly subjective and not very precise or quantitative expression. Interesting in what sense? I would term this a "sentence of no value", i.e. one that conveys not useful information to the reader.}
However, once correcting the RVs from stellar activity signal using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar. The precision on the asymmetric parameter derived from the SN is also 15\% better than the one derived on the common Bisector Inverse Slope Span (BIS SPAN). Besides all these advantages, the errors on the RVs measured by the SN are 60\% greater. 
\comment{To me this statement alone tells me that the SN method is not very useful, and not one that I would use. Any method that produces larger errors *before* correcting for the activity is not a very useful method. Why should the reader continue beyond this point?}
This is not a problem at signal-to-noise ratio levels $>$ 150 because other noise sources dominate in this regime, however we have to be careful when deriving precise RVs for low SNR measurements. We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.
We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.
\comment{You simply cannot make this claim. What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity. You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc. Where is the sensitivity in actually getting out useful information? Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method. I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
Grammatically this is an ambiguous statement. Are you looking for "better signals", i.e. ones that you like, or probing stellar signals in a better way? (This is what you meant, but not what was stated.)}
